On g~0~

### 2017-03-27 manuscript.Rmd
fixed broken refs

[@medlyn_reconciling_2011] does not develop theory for g~0~, instead adds it as a minimum conductance because that's how it is!

@@

The difficulty of this can be seen from the fact that a) many studies set g0 to something rather than fitting it (e.g. @leuning1995 uses 0.01 for all); presumably because unreliable estimates were obtained, b) negative fitted values are common [@leuning1995; @herault2013; @miner2016].

Barnard and Bauerle said so too but gave no details.
Even in very good datasets, g0 and g1 are strongly correlated (Figure 2).
Across datasets, g0 increases when the model fits poorly (Figure 3), and the width of the confidence interval increases when less variation in a ball-berry coefficient.
Often g0 is even negative [@heroult2013; @leuning_modelling_1990], so it is often set to some arbitrary value

When fitting a Ball-Berry type model, negative values are quite common. A typical approach is to avoid this by setting some value based on guesswork [e.g. @leuning_modelling_1990], which we assume is quite common when inspecting the many rounded values in the review by

>>>>

[@medlyn2011] does not develop theory for g~0~, instead adds it as a minimum conductance because that's how it is!

@@

The difficulty of this can be seen from the fact that a) many studies set g0 to something rather than fitting it (e.g. @leuning1995 uses 0.01 for all); presumably because unreliable estimates were obtained, b) negative fitted values are common [@leuning1995; @heroult2013; @miner2016].

Barnard and Bauerle said so too but gave no details.
Even in very good datasets, g0 and g1 are strongly correlated (Figure 2).
Across datasets, g0 increases when the model fits poorly (Figure 3), and the width of the confidence interval increases when less variation in a ball-berry coefficient.
Often g0 is even negative [@heroult2013; @leuning1990], so it is often set to some arbitrary value

When fitting a Ball-Berry type model, negative values are quite common. A typical approach is to avoid this by setting some value based on guesswork [e.g. @leuning1990], which we assume is quite common when inspecting the many rounded values in the review by
